%-------------------------
% Resume in Latex
% Author : Samantha Murray Tuesta
% From template by : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Samantha Murray Tuesta} \\ \vspace{1pt}
    Computer Science Undergraduate and Researcher\\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ (206)747-4546 ~ \href{mailto:smurraytuesta@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{smurraytuesta@gmail.com}} ~ 
    \href{https://linkedin.com/in/sammurraytuesta/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/sammurraytuesta}}  ~
    \href{https://github.com/sammurraytuesta}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/sammurraytuesta}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Western Washington University}{Sep. 2019 -- June 2023}
      {Bachelor of Science in Computer Science, Internet Resource Creation and Management Minor}{Bellingham, WA}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{2}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item \small Formal Languages and Functional Programming
                \item Data Structures
                \item Fundamentals of Web Site Development and Management
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
      
    \resumeSubheading
      {Western Washington University}{July 2020 -- Present}
      {Research Assistant}{Bellingham, WA}
      \resumeItemListStart
        \resumeItem{Undergraduate Research Assistant under Dr. Caroline Hardin, developing an interactive narrative broadening the scope in which we teach digital privacy.} \resumeItem{Focus on elementary to undergraduate level education, transforming socially negotiated digital privacy norms. Lesson plan currently in development to educate young minds into becoming digital privacy and technology stewards.}
      \resumeItemListEnd
      
     
    \resumeSubheading
      {Interns GDL}{June 2021 -- July 2021}
      {Volunteer}{Guadalajara, Jalisco}
      \resumeItemListStart
        \resumeItem{Workshop technical interview best practices, provide resume building assistance, and promote global networking} \resumeItem{Lead weekly coding exercises for a comprehensive review of data structures and algorithms}
      \resumeItemListEnd
      
    \resumeSubheading
      {Google}{Feb. 2021 -- May 2021}
      {Software Product Sprint Participant}{Seattle, WA}
      \resumeItemListStart
        \resumeItem{Collaborated with a team of peers to design and implement a Chrome Extension using JavaScript, HTML, and CSS over the course of 10 weeks.}
        \resumeItem{ Contributed to open source software, conducted code reviews, participated in distributed development, designed new components and interfaces, and lead them to completion.}
      \resumeItemListEnd

    \resumeSubheading
      {Western Washington University}{Jan. 2021 -- March 2021}
      {Internet Studies Intern}{Bellingham, WA}
      \resumeItemListStart
        \resumeItem{Led in the original creation of the Internet Dashboard: a digital archive of the world's leading data.}
        \resumeItem{Extracted real-time analytics and developed PHP queries to pull and visualize data.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/rjkroege/sps7squared}{\raisebox{-0.2\height}Seminar Extension}} $|$ \emph{JavaScript, Firebase, HTML, CSS}}{March 2021 -- Present}
          \resumeItemListStart
            \resumeItem{A Google Chrome note-taking extension allowing for cross-website note creation.} \resumeItem{All notes are stored using firebase authentication services and fetched from the database to be shown on its associated website and URL.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{\href{https://carolinehardin.github.io/DigitalPrivacyDetectives/}{\raisebox{-0.2\height}Digital Privacy Detectives}} $|$ \emph{Twine, JavaScript, jQuery, HTML, CSS}}{July 2020 -- Present}
          \resumeItemListStart
            \resumeItem{Led in the dynamic design and implementation of $6$ HTML pages and the creation of $6$ external stylesheets for over $60$ commits to GitHub.} \resumeItem{Actively engaging in a group of $4-5$ participants every week to discuss progress as well as problem-solve any issues that arise.}
          \resumeItemListEnd 
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{\href{https://gitlab.com/noah-hance/internet-dashboard}{\raisebox{-0.2\height}Internet Dashboard}} $|$ \emph{amCharts, JavaScript, PHP, HTML, CSS}}{Jan. 2021 -- March 2021}
          \resumeItemListStart
            \resumeItem{An independent project within Western Washington University's Internship in Internet Studies Program.}
            \resumeItem{Taking the pulse of the internet and displaying it in what could be considered the "front page of the internet.”}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}

%
%-----------PROGRAMMING SKILLS-----------
\section{Relevant Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Java, Python, HTML, CSS, JavaScript, jQuery, JSON, C, PHP, SQL, MySQL, Databases, LaTeX, Git} \\
     \textbf{Developer Tools}{: VS Code, Google Cloud Shell, Twine} \\
     \textbf{Languages}{: English, Spanish}
    }}
 \end{itemize}
 \vspace{-16pt}

\end{document}
